---
title: "ML Results"
date: "`r Sys.Date()`"
output:
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
schtools::set_knitr_opts()
```

```{r load}
library(knitr)
```

Machine learning algorithms used were `r snakemake@params[['ml_methods']]`.
Models were trained with `r snakemake@params[['nseeds']]` different random
partitions of the `r snakemake@params[['dataset']]` dataset into training and
testing sets using `r snakemake@params[['kfold']]`-fold cross validation.

## Model Performance

```{r perf_plot, out.width='80%'}
include_graphics(snakemake@input[['perf_plot']])
```

## Feature Importance

```{r feat_imp_plot, out.width='80%'}
include_graphics(snakemake@input[['feat_plot']])
```

## Memory Usage & Runtime

```{r runtime_plot, out.width='80%'}
include_graphics(snakemake@input[['bench_plot']])
```

Each model training run was given `r snakemake@params[['ncores']]` cores
for parallelization.

## Hyperparameter Performance

```{r hp_plot, out.width='80%'}
include_graphics(snakemake@input[['hp_plot']])
```