---
title: "ML Results"
date: "`r Sys.Date()`"
output:
  html_document:
    keep_md: true
    self_contained: true
    theme: spacelab
---

```{r setup, include=FALSE}
schtools::set_knitr_opts()
```

```{r load}
library(knitr)
```

Machine learning algorithm(s) used: `r snakemake@params[['ml_methods']]`.
Models were trained with `r snakemake@params[['nseeds']]` different random
partitions of the `r snakemake@params[['dataset']]` dataset into training and
testing sets using `r snakemake@params[['kfold']]`-fold cross validation.
See [`r snakemake@params[['config_path']]`](`r snakemake@params[['config_path']]`) 
for the full configuration.

## Workflow

```{r rulegraph, out.width = '80%'}
include_graphics(snakemake@input[['rulegraph']])
```

## Model Performance

```{r perf_plot, out.width='80%'}
include_graphics(snakemake@input[['perf_plot']])
```

```{r roc_plot, out.width='80%'}
include_graphics(snakemake@input[['roc_plot']])
```

## Hyperparameter Performance

```{r hp_plot, out.width='80%'}
include_graphics(snakemake@input[['hp_plot']])
```

```{r feat_imp_header, results='asis'}
if (isTRUE(snakemake@params[['find_feature_importance']])) { 
    cat("## Feature Importance") 
}
```

```{r feat_imp_plot, out.width='80%', eval=snakemake@params[['find_feature_importance']]}
include_graphics(snakemake@input[['feat_plot']])
```

## Memory Usage & Runtime

Each model training run was given `r snakemake@params[['ncores']]` cores
for parallelization.

```{r runtime_plot, out.width='80%'}
include_graphics(snakemake@input[['bench_plot']])
```
